The human in the loop: volunteer computing as a socio-technical system

### 2016-02-29 Alife16/paper.tex
More typos and suggestions in results section, although it has been already submitted :P

Figure \ref{fig:system} describes the general system architecture and
algorithm behavior. Different web technologies, such as JQuery or {\tt
  Chart.js} have been used to build the user interface elements of the
framework, a part of which is shown in Figure \ref{fig:screenshot} and
should be running in \url{http://nodio-jmerelo.rhcloud.com}.

\begin{figure}[!t]
\centering
\includegraphics[width=0.95\linewidth]{nodio-screenshot.png}
\caption{Screenshot showing the fitness and number of users as seen by
volunteers. The one on the left shows fitness, on the right the
accumulated number of users. \label{fig:screenshot}}
\end{figure}
%
\begin{figure}[!t]
\centering
\includegraphics[width=3in]{system.pdf}
\caption{Description of the proposed system. Clients execute a JavaScript EA
  in the browser, which, every 100 generations, sends the best
  individual and receives a random one back from the server.}
\label{fig:system}
\end{figure}

@@

\begin{table}[htb]
\caption{Experiment table, with summary of results. \label{tab:runs}}
\begin{center}
\begin{tabular}{l|rrl}
\hline
Experiment & \#Runs & Different IPs & Traps \\
\hline
April 4th 4/4 & 57 & 191 & 40 \\
April 24th 4/24 &  231 & 559& 40  \\
July 31th 7/31 & 97 & 179 & 40 \\
\hline
February, cache=128 & 61 & 75 & 50  \\
February, cache=64 & 61 & 220 & 50  \\
February, cache=32 & 39 & 86 & 50  \\
% grep start ~/Code/splash-volunteer/data/2016/nodio-2016-2-28-cache=32.log
\hline
\end{tabular}
\end{center}
\end{table}
%
Initial experiments were set up using the OpenShift
PaaS, which provides a free tier, making the whole experiment cost
equal to \$0.00. Experiments were
announced through a series of posts in Twitter and, in the latest case, Telegram, and
results were published here \citep{DBLP:conf/gecco/GuervosG15}. For the
purpose of this paper, we repeated the announcement several times
through the month of February. All  %% April --> January ??
in all, we have the set of runs with the characteristics shown in
Table \ref{tab:runs}. In general, every experiment took several
days. No particular care was taken about the time of the announcement
or the particular wording. Every {\em experiment} consisted in running
until the solution of the 50-trap problem was found. When the correct
solution was sent to the server, the counter was updated and the pool
of solutions reset to the void set. There was no special intention to wait
until all clients had finished, thus it might happen that, in fact,
the islands running in the browser {\em spill} from one experiment to
the next. However, previous experiments have proven that the influence
of these islands in the next experiment is indeed negligible.

The table shows that every run included more than 30 experiments. The
number of different IPs intervening in them varied from more than one
hundred to more than five hundred in the second experiment, with a
number around 50 in the second, and most recent, batch of experiments. 
%
\begin{table}[htb]
\caption{Summary of time per run, number of IPs and number of {\tt
    PUT}s per IP in the initial runs. \label{tab:summary:os}}
\begin{center}
\begin{tabular}{l|cccc}
\hline
     & \multicolumn{2}{c}{IPs} & \multicolumn{2}{c}{Median} \\
Experiment & Median & Max & time (s) &  \#{\tt  PUT}s \\
\hline
4/4 & 5 & 16 & 2040 & 18   \\
4/24 &  5 & 29 & 732 & 11  \\
7/31 & 5 & 14 & 260 & 23   \\
\hline
Cache=128 & 5 & 17 & 222.2 & 124 \\ 
Cache=64 & 8 & 38 & 51.3 & 100 \\
Cache=32 & 6 & 19 & 58.9 & 45 \\
\hline
% Data in .RData file in Splash-volunteer
\end{tabular}
\end{center}
\end{table}
%

@@

We will have to analyze differently the median time, since the two
batches are solving different problems. In both cases it possesses a
big range of variation, but 50\% of 
the time takes less than several minutes, from around 4 minutes in the
best case to roughly 2/3 of an hour in the worst case. Remarkably
enough, the time is more consistent in the second batch and always
around one minute, in two cases even less, and that happens when the
median number of IPs is higher. It should be noted that while the
first batch of experiments took several days in each case, the second
only lasted for a few hours, with a more continued effort of
publicizing it in social networks; this is specially true in the
case of cache equal to 64, which is noticed by the high number of
volunteers participating in the experiment. The conclusion is that,
in general, the key factor in the time needed to find the solution
is, as expected, the number of volunteers it is able to gather on a
short notice.

The number of {\tt PUTs}, every one corresponding to 100 generations,
is the algorithmic result. It is relatively unchanged for the first
batch and around 20, that is, 2000 generations or 2000*128 = 256000
evaluations. In this case, an ``unlimited'' cache was used, with all
individuals sent from clients stored until the end of the
experiment. However, we were interested in measuring also the
performance of the algorithm itself by changing the cache size, after
making it limited. As it can be seen in the table, there is a clear
change in the number of evaluations needed, with smaller cache sizes
producing solutions in less evaluations, until it is for the cache
size = 32 roughly twice as much as with the previous problem, with 40
traps. This is a good result and is also algorithmically consistent
with other results obtained using the same type of problems. Since in
this paper we were interested in leveraging the user's CPU cycles by
improving the algorithm, a good conclusion of this paper is that
having a small pool size helps clients to obtain ``good'' individuals
from the pool, as opposed to any individual that could be obtained
before. Besides, cache policy deletes the oldest individuals, which
makes those in the pool be {\em current}, helping then newcomers and
any participant obtain the best individuals found in the last part of
the experiment. Besides, a limited cache helps also in cases with a
bigger search space or longer running times when the server simply
crashed due to lack of RAM.

@@

That is why we used a more difficult problem in the second batch of
experiments, which is shown in bottom row of Figure
\ref{fig:duration}. The pattern is remarkably similar, showing a
positive correlation between the time for solving the problem and the
number of computers, at least for cache sizes 128 and 64. However, it
is interesting to observe that, for cache=32, the time needed to find
the solution decreases from one to approximately 4-5 nodes, to then
increase for a higher number of participating computers, distinguished
by IP. The green dot at the bottom is probably and outlier that we
will try to explain later on. This leads us to conclude that a better
amount of computers might contribute to speed up the solution, if the
time the experiment ideally takes is sufficient, that is, of the order of a
minute, and enough volunteers concur simultaneously. This is also
observed, not so clearly, in the case of cache=64, with an interval of
around 10 IPs obtaining less time than experiments with less or more
IPs, and of the same order, between 10 and 100 seconds. If we look at
the graph that shows the number of IPs or volunteers per minute for
this experiment, shown in Figure \ref{fig:otisdriftwood}, we see that
there are peaks of more than 25 volunteers, and a period of several
hours with a minimum of 6 computers and peaks of more than 10. The
long period after midnight where there is a single volunteer left
masks the success achieved during this set of experiments, from which
we draw two lessons: first, you need a social network influencer to
announce your experiments and second, no matter what, do not do any
experiment after midnight. This statement, which might seem tongue in
cheek, in fact it is a conclusion drawn from the experimental data and
to what extent the social network is an essential part of the
description and performance of the NodIO volunteer computing system.

\begin{figure}[!htb]
\centering
\includegraphics[width=0.32\linewidth]{time-vs-rank-OS-4-4.png}
\includegraphics[width=0.32\linewidth]{time-vs-rank-OS-4-24.png}
\includegraphics[width=0.32\linewidth]{time-vs-rank-OS-7-31.png}
\includegraphics[width=0.32\linewidth]{time-vs-rank-alife-128.png}
\includegraphics[width=0.32\linewidth]{time-vs-rank-alife-64.png}
\includegraphics[width=0.32\linewidth]{time-vs-rank-alife-32.png}
\caption{Duration of experiments vs. rank, with $y$ axis in a
  logarithmic scale. Dot color is related to the number of IPs
  participating in the experiment. From left to right and top to bottom, experiments
  4/4, 4/24 and 7/31 and caches=128,64, 32} 
\label{fig:zipf:os}
% First ones made with time-vs-IPs-openshift.R:  
\end{figure}
%
It is also interesting to check the distribution of the experiment
duration, shown in Figure \ref{fig:zipf:os} and which roughly follows
a Zipf's law, with similar distribution along all three runs. The 4/24
run is the most complete and shows a S-shape, which implies an
accumulation of experiments taking similar time and around 100
seconds; this S-shape appears too in the experiments with cache=128
(bottom row, left). The most interesting part is the {\em tail}, which shows how
many experiments took a desirable amount of time, of the order of
10 seconds, and which appears in all three graphs. As it can be seen,
it sharply drops implying there are 
just a few of them, and with diminishing probability as time
decreases. However, since they have a greenish color, implying a low
number of IPs, they might be due to clients {\em carrying over} from
the previous one. This is a characteristic of this implementation
which will be examined later on, but at any rate if we discard those
experiments that take too much or too little, there is a decreasing
exponential distribution that corresponds to the Zipf's law.

\begin{figure}[!htb]
\centering
\includegraphics[width=0.32\linewidth]{weibull-puts-openshift-4-4.png}
\includegraphics[width=0.32\linewidth]{weibull-puts-openshift-4-24.png}
\includegraphics[width=0.32\linewidth]{weibull-puts-openshift-7-31.png}
\includegraphics[width=0.32\linewidth]{weibull-fit-cache=128.png}
\includegraphics[width=0.32\linewidth]{weibull-fit-cache=64.png}
\includegraphics[width=0.32\linewidth]{weibull-fit-cache=32.png}
\caption{Number of {\tt PUT}s per unique IP and fit to a Weibull
  distribution (in red). From left to right and top to bottom, experiments
  4/4, 4/24 and 7/31 and new experiments with cache=128, 64, 32.} 
% Plotted with ../data/plot-zipf-openshift.R
\label{fig:puts:os}
\end{figure}
%
A similar exponential distribution also appears if we rank HTTP {\tt
  PUT}s, equivalents to the number of 
generations divided by 100, or to evaluations divided by 12800,
contributed by every user, which is shown 
in Figure \ref{fig:puts:os}. These results show a Zipf-like behavior,
that is, a power law with a small {\em bump} in the lowest
values. After testing the Generalized Extreme Value distribution and
failing for the new batch of experiments, we have fitted it to a
Weibull distribution \cite{thoman1969inferences} with the resulting
parameters shown in Table \ref{tab:puts:os}. 
%
\begin{table}
\caption{Weibull distribution  parameters of the fit of
  the number of {\tt PUT}s per unique IP. \label{tab:puts:os}}
\begin{center}
\begin{tabular}{l|cc}
\hline
Experiment  &  Scale $\sigma$ & Shape $\xi$ \\
\hline
4/4 &  43.07 $\pm$ 5.80 &  0.57 $\pm$ 0.03 \\
4/24 & 22.97 $\pm$ 1.57 & 0.66 $\pm$  0.02  \\
7/31 &  53.18 $\pm$ 7.77 &  0.54 $\pm$ 0.03   \\
\hline
Cache 128 & 205.28 $\pm$ 32.10 & 0.77 $\pm$ 0.07 \\ 
Cache 64 & 178.99 $\pm$ 36.44 & 0.60 $\pm$ 0.05 \\ 
Cache 32 & 168.15 $\pm$ 49.28 & 0.57 $\pm$ 0.07 \\
\hline
% from plot-zipf-openshift.R and ips-puts-alife.R
\end{tabular}
\end{center}
\end{table}
%
The inverse
Weibull distribution is a special case of the GEV distribution we have
used in those papers, and appears usually in natural sciences and
artificial life, usually related to decay. I has been frequently
fitted to volunteer computing frameworks such as SETI@home
\citep{javadi2009mining}. The model that user behavior follows can be
explained straighforwardly: when users visit the page, it draws their
attention for a limited amount of time. They give it a chance for a
few seconds. If something there amuses them or they can engage in a
conversation about it, they stay for a while longer, otherwise, they
leave. The {\em scale} parameter, which is around 20-40 in the first
batch for the 40 Trap problem and betwen 160 and 200 in the 60 traps
problem, depends mainly on the maximum number of generations people
leave it running. Since it finishes or stalls after a number of
generations shown in Figure \ref{tab:summary:os}, volunteer just
leave after that. Curiously enough, the scale parameter is roughly
twice the median number of {\tt PUT}s per experiment, showing that, on
average, the most loyal users reload the page twice after finishing or
after seeing the evolution does not progress. This rule of thumb
breaks down with the last experiment, however, which is interesting by
itself, too.

The slope or shape parameter, on the other hand, indicates the overall
shape of the curve. A value less than 1 indicates a concave (in an
non-algorithmic scale) curve,
with figures closer to one indicating a smaller slope. In all cases
values are between 0.54 and 0.77, independently of the experiment. It
might be the case that this number depends more on the total number of
experiments carried out, with sets with more experiments, both in the
middle, having values between 0.60 and 0.70. The distribution is
remarkably similar which gives us a model of user behavior that is, to
a certain extent, independent of the experiment.

>>>>

Figure \ref{fig:system} describes the general system architecture and
algorithm behavior. Different web technologies, such as JQuery or {\tt
  Chart.js} have
been used to build the user interface elements of the framework.

\begin{figure}[!t]
\centering
\includegraphics[width=3in]{system.pdf}
\caption{Description of the proposed system. Clients execute a JavaScript EA
  in the browser, which, every 100 generations, sends the best
  individual and receives a random one back from the server.}
\label{fig:system}
\end{figure}

@@

\begin{table}[htb]
\caption{Experiment table, with summary of results. \label{tab:runs}}
\begin{center}
\begin{tabular}{l|rrl}
\hline
Experiment & \#Runs & Different IPs & Traps \\
\hline
April 4th 4/4 & 57 & 191 & 40 \\
April 24th 4/24 &  231 & 559& 40  \\
July 31th 7/31 & 97 & 179 & 40 \\
\hline
February, cache=128 & 61 & 75 & 50  \\
February, cache=64 & 61 & 220 & 50  \\
February, cache=32 & 39 & 86 & 50  \\
% grep start ~/Code/splash-volunteer/data/2016/nodio-2016-2-28-cache=32.log
\hline
\end{tabular}
\end{center}
\end{table}
%
Initial experiments were set up using the OpenShift
PaaS, which provides a free tier, making the whole experiment cost
equal to \$0.00. Experiments were
announced through a series of posts on Twitter and, in the latest case, Telegram, and
results were published here \citep{DBLP:conf/gecco/GuervosG15}. For the
purpose of this paper, we repeated the announcement several times
through the month of February. All  %% April --> January ??
in all, we have the set of runs with the characteristics shown in
Table \ref{tab:runs}. In general, every experiment took several
days. No particular care was taken about the time of the announcement
%Pablo: but it would great at least describe how many times was announced and how long
or the particular wording. Every {\em experiment} consisted in running
until the solution of the 50-trap problem was found. When the correct
solution was sent to the server, the counter was updated and the pool
of solutions resets to the void set. There was no special intention to wait
until all clients had finished, thus it might happen that. In fact,
the islands running in the browser {\em spill} from one experiment to
the next. However, previous experiments have proven that the influence
of these islands in the next experiment is indeed negligible. %Pablo: cite

The table shows that every run included more than 30 experiments. The
%Pablo: reference to table? (maybe the final print will misplace it)
number of different IPs intervening in them varied from more than one
hundred to more than five hundred in the second experiment, with a
number around 50 in the second, and most recent, batch of experiments. 
%
\begin{table}[htb]
\caption{Summary of time per run, number of IPs and number of {\tt
    PUT}s per IP in the initial runs. \label{tab:summary:os}}
\begin{center}
\begin{tabular}{l|cccc}
\hline
     & \multicolumn{2}{c}{IPs} & \multicolumn{2}{c}{Median} \\
Experiment & Median & Max & time (s) &  \#{\tt  PUT}s \\
\hline
4/4 & 5 & 16 & 2040 & 18   \\
4/24 &  5 & 29 & 732 & 11  \\
7/31 & 5 & 14 & 260 & 23   \\
\hline
Cache=128 & 5 & 17 & 222.2 & 124 \\ 
Cache=64 & 8 & 38 & 51.3 & 100 \\
Cache=32 & 6 & 19 & 58.9 & 45 \\
\hline
% Data in .RData file in Splash-volunteer
\end{tabular}
\end{center}
\end{table}
%

@@

We will have to analyze differently the median time, since the two
%Pablo: different verbal times ("will have", and before, "is shown"). Homogenize.
batches are solving different problems. In both cases it possesses a
big range of variation, but 50\% of 
the time takes less than several minutes, from around 4 minutes in the
best case to roughly 2/3 of an hour in the worst case. Remarkably
enough, the time is more consistent in the second batch and always
around one minute, in two cases even less, and that happens when the
median number of IPs is higher. It should be noted that while the
first batch of experiments took several days in each case, the second
only lasted for a few hours, with a more continued effort of
publicizing it in social networks. This is specially true in the
%Pablo: removed semicolon before "This". @unintendedbear does not like them :P
case of cache equal to 64, which is noticed by the high number of
volunteers participating in the experiment. The conclusion is that,
in general, the key factor in the time needed to find the solution
is, as expected, the number of volunteers it is able to gather on a
short notice.

The number of {\tt PUTs}, every one corresponding to 100 generations,
is the algorithmic result. It is relatively unchanged for the first
batch and around 20, that is, 2000 generations or 2000*128 = 256000
evaluations. In this case, an ``unlimited'' cache was used, with all
individuals sent from clients stored until the end of the
experiment. However, we were interested in measuring also the
performance of the algorithm itself by changing the cache size, after
making it limited. As it can be seen in the table, there is a clear
%Pablo: which table?
change in the number of evaluations needed, with smaller cache sizes
producing solutions in less evaluations, until it is for the cache
size = 32 roughly twice as much as with the previous problem, with 40
traps. This is a good result and is also algorithmically consistent
with other results obtained using the same type of problems. Since in
this paper we were interested in leveraging the user's CPU cycles by
improving the algorithm, a good conclusion of this paper is that
having a small pool size helps clients to obtain ``good'' individuals
from the pool, as opposed to any individual that could be obtained
before. Besides, cache policy deletes the oldest individuals, which
makes those in the pool be {\em current}, helping then newcomers and %Pablo: "then helping newcomers", instead?
any participant obtain the best individuals found in the last part of
the experiment. Besides, a limited cache helps also in cases with a
bigger search space or longer running times when the server simply
crashed due to lack of RAM.

@@

That is why we used a more difficult problem in the second batch of
experiments, which is shown in the bottom row of Figure
\ref{fig:duration}. The pattern is remarkably similar, showing a
positive correlation between the time for solving the problem and the
number of computers, at least for cache sizes 128 and 64. However, it
is interesting to observe that, for cache=32, the time needed to find
the solution decreases from one to approximately 4-5 nodes, to then
increase for a higher number of participating computers, distinguished
by IP. The green dot at the bottom is probably an outlier that we
will try to explain later on. This leads us to conclude that a better
amount of computers might contribute to speed up the solution, if the
time the experiment ideally takes is sufficient, that is, of the order of a
minute, and enough volunteers concur simultaneously. This is also
observed, not so clearly, in the case of cache=64, with an interval of
around 10 IPs obtaining less time than experiments with less or more
IPs, and of the same order, between 10 and 100 seconds. If we look at
the graph that shows the number of IPs or volunteers per minute for
this experiment, shown in Figure \ref{fig:otisdriftwood}, we see that
there are peaks of more than 25 volunteers, and a period of several
hours with a minimum of 6 computers and peaks of more than 10. The
long period after midnight where there is a single volunteer left
masks the success achieved during this set of experiments, from which
we draw two lessons: first, you need a social network influencer to
%Pablo: people know the meaning of "influencer"? Probably yes, but I mention it just in case.
announce your experiments and second, no matter what, do not do any
experiment after midnight. This statement, which might seem tongue in
cheek, in fact, it is a conclusion drawn from the experimental data and
to what extent the social network is an essential part of the
description and performance of the NodIO volunteer computing system.

\begin{figure}[!htb]
\centering
\includegraphics[width=0.32\linewidth]{time-vs-rank-OS-4-4.png}
\includegraphics[width=0.32\linewidth]{time-vs-rank-OS-4-24.png}
\includegraphics[width=0.32\linewidth]{time-vs-rank-OS-7-31.png}
\includegraphics[width=0.32\linewidth]{time-vs-rank-alife-128.png}
\includegraphics[width=0.32\linewidth]{time-vs-rank-alife-64.png}
\includegraphics[width=0.32\linewidth]{time-vs-rank-alife-32.png}
\caption{Duration of experiments vs. rank, with $y$ axis in a
  logarithmic scale. Dot color is related to the number of IPs
  participating in the experiment. From left to right and top to bottom, experiments
  4/4, 4/24 and 7/31 and caches=128,64, 32} 
\label{fig:zipf:os}
% First ones made with time-vs-IPs-openshift.R:  
\end{figure}
%
It is also interesting to check the distribution of the experiment
duration, shown in Figure \ref{fig:zipf:os} and which roughly follows
a Zipf's law, with similar distribution along all three runs. The 4/24
run is the most complete and shows an S-shape, which implies an
accumulation of experiments taking similar time and around 100
seconds; this S-shape appears too in the experiments with cache=128
(bottom row, left). The most interesting part is the {\em tail}, which shows how
many experiments took a desirable amount of time, on the order of
10 seconds, and which appears in all three graphs. As it can be seen,
it sharply drops implying there are 
just a few of them, and with diminishing probability as time
decreases. However, since they have a greenish color, implying a low
number of IPs, they might be due to clients {\em carrying over} from
the previous one. This is a characteristic of this implementation
which will be examined later on, but at any rate, if we discard those
experiments that take too much or too little, there is a decreasing
exponential distribution that corresponds to the Zipf's law.

\begin{figure}[!htb]
\centering
\includegraphics[width=0.32\linewidth]{weibull-puts-openshift-4-4.png}
\includegraphics[width=0.32\linewidth]{weibull-puts-openshift-4-24.png}
\includegraphics[width=0.32\linewidth]{weibull-puts-openshift-7-31.png}
\includegraphics[width=0.32\linewidth]{weibull-fit-cache=128.png}
\includegraphics[width=0.32\linewidth]{weibull-fit-cache=64.png}
\includegraphics[width=0.32\linewidth]{weibull-fit-cache=32.png}
\caption{Number of {\tt PUT}s per unique IP and fit to a Weibull
  distribution (in red). From left to right and top to bottom, experiments
  4/4, 4/24 and 7/31 and new experiments with cache=128, 64, 32.} 
% Plotted with ../data/plot-zipf-openshift.R
\label{fig:puts:os}
\end{figure}
%
A similar exponential distribution also appears if we rank HTTP {\tt
  PUT}s, equivalents to the number of 
generations divided by 100, or to evaluations divided by 12800,
contributed by every user, which is shown 
in Figure \ref{fig:puts:os}. These results show a Zipf-like behavior,
that is, a power law with a small {\em bump} in the lowest
values. After testing the Generalized Extreme Value distribution and
failing for the new batch of experiments, we have fitted it to a
Weibull distribution \cite{thoman1969inferences} with the resulting
parameters shown in Table \ref{tab:puts:os}. 
%
\begin{table}
\caption{Weibull distribution  parameters of the fit of
  the number of {\tt PUT}s per unique IP. \label{tab:puts:os}}
\begin{center}
\begin{tabular}{l|cc}
\hline
Experiment  &  Scale $\sigma$ & Shape $\xi$ \\
\hline
4/4 &  43.07 $\pm$ 5.80 &  0.57 $\pm$ 0.03 \\
4/24 & 22.97 $\pm$ 1.57 & 0.66 $\pm$  0.02  \\
7/31 &  53.18 $\pm$ 7.77 &  0.54 $\pm$ 0.03   \\
\hline
Cache 128 & 205.28 $\pm$ 32.10 & 0.77 $\pm$ 0.07 \\ 
Cache 64 & 178.99 $\pm$ 36.44 & 0.60 $\pm$ 0.05 \\ 
Cache 32 & 168.15 $\pm$ 49.28 & 0.57 $\pm$ 0.07 \\
\hline
% from plot-zipf-openshift.R and ips-puts-alife.R
\end{tabular}
\end{center}
\end{table}
%
The inverse
Weibull distribution is a special case of the GEV distribution we have
used in those papers, and appears usually in natural sciences and
artificial life, usually related to decay. It has been frequently
fitted to volunteer computing frameworks such as SETI@home
\citep{javadi2009mining}. The model that user behavior follows can be
explained straighforwardly: when users visit the page, it draws their
attention for a limited amount of time. They give it a chance for a
few seconds. If something there amuses them or they can engage in a
conversation about it, they stay for a while longer, otherwise, they
leave. The {\em scale} parameter, which is around 20-40 in the first
batch for the 40 Trap problem and between 160 and 200 in the 60 traps
problem, depends mainly on the maximum number of generations people
leave it running. Since it finishes or stalls after a number of
generations shown in Figure \cite{tab:summary:os}, volunteer just
leaves after that. Curiously enough, the scale parameter is roughly
twice the median number of {\tt PUT}s per experiment, showing that, on
average, the most loyal users reload the page twice after finishing or
after seeing the evolution does not progress. This rule of thumb
breaks down with the last experiment, however, which is interesting by
itself, too.

The slope or shape parameter, on the other hand, indicates the overall
shape of the curve. A value less than 1 indicates a concave (in a
non-algorithmic scale) curve,
with figures closer to one indicating a smaller slope. In all cases
values are between 0.54 and 0.77, independently of the experiment. It
might be the case that this number depends more on the total number of
experiments carried out, with sets with more experiments, both in the
middle, having values between 0.60 and 0.70. The distribution is
remarkably similar which gives us a model of user behavior that is, to
a certain extent, independent of the experiment.
